### 2018-06-13 express2018/equa.tex
text
Stage work
A little more compression, release all locks except "bisim"
compression

\begin{definition}
Assume that, for each $i$ of 
 a countable indexing set $I$, we have variables $X_i$, and expressions
$E_i$ possibly containing  such variables. 
Then 
$$\{  X_i = E_i\}_{i\in I}$$
is 
  a \emph{system of equations}. (There is one equation for each variable $X_i$.)
\qed\end{definition}

We write $E[\til P]$ for the expression resulting from $E$ by
replacing each variable $X_i$   with the process $P_i$, assuming
$\til P$ and $\til X$ have the same length. (This is syntactic
replacement.) 
% The components of $\til P$ need not be
%  different from each other, as it must be for the variables $\til X$.
% If the system has infinitely many equations,
% the  tuples $\til P$ and $\til X$
%  are infinite too.
\begin{definition}
Suppose  $\{  X_i = E_i\}_{i\in I}$ is a system of equations: 
\begin{itemize}
\item
 $\til P$ is a \emph{solution of the 
system of equations  for $\wb$} 
if for each $i$ it holds
that $P_i \wb E_i [\til P]$.

\item the  system has 
\emph{a unique solution for $\wb$}  if whenever 
 $\til P$ and $\til Q$ are both solutions for $\wb$, then $\til P \wb
 \til Q$. \qed
\end{itemize} 
 \end{definition}

@@

For instance, the solution of the equation 
$ X = a. X$ 
is  the process
$R \defi \recu A . a A$, and   for any other solution $P$ we have $P \wb R$.
In contrast, the equation 
 $X = a|  X$ has solutions that may be quite different, namely any process capable of
continuosly  performing $a$ action (but that could behave arbitrarily  on other actions).

@@

\item 
 \emph{sequential} if,  in each    $E_i$, each occurrence of
an \behav\  variable only appears  underneath prefixes and sums.
\qed\end{itemize}
 \end{definition}

@@

\begin{theorem}[unique solution of equations, \cite{Mil89}]
\label{t:Mil89}
A system of guarded and sequential equations
% $\{  X_i = E_i\}_{i\in I}$ 
   has 
a unique solution
 for $\wb$. \qed
\end{theorem}

% The proof exploits an invariance property on immediate transitions for
% guarded and sequential expressions, and then extracts a bisimulation
% (up-to bisimilarity) out
% of the solutions of the system.  
To see the  need of the
 sequentiality  condition, 
  consider
 the equation (from \cite{Mil89}) 
\[ X = \res a (a. X | \outC a) \]
where $X$ is guarded but not sequential. Any processes that does
not use  $a$
 is a solution.

>>>>

\begin{definition}
Assume that, for each $i$ of 
 a countable indexing set $I$, we have variables $X_i$, and expressions
$E_i$ possibly containing  such variables. 
Then 
$$\{  X_i = E_i\}_{i\in I}$$
is 
  a \emph{system of equations}. (There is one equation for each variable $X_i$.)
\end{definition}

We write $E[\til P]$ for the expression resulting from $E$ by
replacing each variable $X_i$   with the process $P_i$, assuming
$\til P$ and $\til X$ have the same length. (This is syntactic
replacement.) 
% The components of $\til P$ need not be
%  different from each other, as it must be for the variables $\til X$.
% If the system has infinitely many equations,
% the  tuples $\til P$ and $\til X$
%  are infinite too.
\begin{definition}
Suppose  $\{  X_i = E_i\}_{i\in I}$ is a system of equations: 
\begin{itemize}
\item
 $\til P$ is a \emph{solution of the 
system of equations  for $\wb$} 
if for each $i$ it holds
that $P_i \wb E_i [\til P]$;

\item it %the  system
 has \emph{a unique solution for $\wb$}  if whenever 
 $\til P$ and $\til Q$ are both solutions for $\wb$, then $\til P \wb
 \til Q$. 
\end{itemize} 
 \end{definition}

@@

For instance, the solution of the equation 
$ X = a. X$ 
is  the process
$R \DSdefi \recu A . a A$, and   for any other solution $P$ we have $P \wb R$.
In contrast, the equation 
 $X = a|  X$ has solutions that may be quite different, namely any process capable of
continuosly  performing $a$ action (but that could behave arbitrarily  on other actions).

@@

\item 
 \emph{sequential} if,  in each    $E_i$, each occurrence of
an \behav\  variable only appears  underneath prefixes and sums.
\end{itemize}
 \end{definition}

@@

\begin{theorem}[unique solution of equations, \cite{Mil89}]
\label{t:Mil89}
A system of guarded and sequential equations
% $\{  X_i = E_i\}_{i\in I}$ 
   has 
a unique solution
 for $\wb$.
\end{theorem}

% The proof exploits an invariance property on immediate transitions for
% guarded and sequential expressions, and then extracts a bisimulation
% (up-to bisimilarity) out
% of the solutions of the system.  
To see the  need of the
 sequentiality  condition, 
  consider
 the equation (from \cite{Mil89}) $X = \res a (a. X | \outC a)$
where $X$ is guarded but not sequential. Any processes that does
not use  $a$
 is a solution.
